### 2025-01-24 scripts/compare-hard-shell-with-accessory.Rmd
new results files with discrepancies for within-range targets

```{r}
# Read in results for RM targets
df_4 = read.csv('~/Downloads/trieste/test_RM_targets_k4.csv')
df_4_filter = df_4[df_4$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_4$discrepancy_selected!="None"],]
df_5 = read.csv('~/Downloads/trieste/test_RM_targets_k5.csv')
df_5_filter = df_5[df_5$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_5$discrepancy_selected!="None"],]
df_6 = read.csv('~/Downloads/trieste/test_RM_targets_k6.csv')
df_6_filter = df_6[df_6$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_6$discrepancy_selected!="None"],]

>>>>

```{r}
# Read in results for RM targets
df_4 = read.csv('../results/rmes_discrepancies_targets_k4.csv')
df_4_filter = df_4[df_4$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_4$discrepancy_selected!="None"],]
df_5 = read.csv('../results/rmes_discrepancies_targets_k5.csv')
df_5_filter = df_5[df_5$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_5$discrepancy_selected!="None"],]
df_6 = read.csv('../results/rmes_discrepancies_targets_k6.csv')
df_6_filter = df_6[df_6$PTU %in% ptu$PTU[ptu$pangenome.category=="include" & df_6$discrepancy_selected!="None"],]
